---
title: "Splitgate Report"
author: "Ryan Poertner"
date: "11/23/2021"
output: html_document

params:
  main_data: "split_big.csv"
  ranked_data: "split_ranked.csv"
  casual_data: "split_casual.csv"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Research Question
## Understanding the phenomenon

**background:** Video game

**goal:** To determine what in-game behaviors influence the odds of winning a match in Splitgate.


# Dataset
## Response

**Win: ** Whether or not the subject won the match. This is binary in nature.

## Explanatory

**Kills: **how many kills the subject had in a match

**Deaths: **how many times the subject died in a match

**Assists: **how many times the subject contributed to killing an opponent without landing the killing shot in a match.

**Headshots Landed: **how many headshots the subject landed on the opposing side.

**Kills Per Minute: **how many kills the subject had per minute.

**Distance Portaled: **cumulative distance traveled by subject(in Meters).

**Portals Spawned: **how many portals the subject created.

**Damage Dealt: **how much damage the subject dealt(in points).

# Exploration of Data


```{r echo = FALSE}
  all_data <- read.csv(params$main_data)
  ranked_data <- read.csv(params$ranked_data)
  casual_data <- read.csv(params$casual_data)
```

The majority of the data appeared either linear or ambiguous in distribution, so I did not perform any transformations. however, I did notice a handful of outliers in headshots landed and distance portaled, so I subsetted the data based on that.


```{r echo = FALSE}
  plot(~Kills+Deaths+Assists+headshotsLanded+killsPerMinute+
       distancePortaled+portalsSpawned+damageDealt,data=all_data)

```

```{r echo = FALSE}

    knitr::kable(summary(all_data)[,-1], caption = "Table of 5 number summary")
```

## SLLR Model

```{r echo = FALSE}

set.seed(121)
train_rows <- sample(length(all_data$Kills), length(all_data$Kills) - (length(all_data$Kills)/3))
split_train <- all_data[train_rows, ]
split_test <- all_data[-train_rows, ]

    data_out <- glm(Win~Kills +  
                   Deaths + 
                   Assists +
                   headshotsLanded + 
                   killsPerMinute + 
                   distancePortaled +
                   portalsSpawned +
                   damageDealt, 
                 data = split_train, family = "binomial")
    
    knitr::kable(summary(data_out)$coefficients[-1,], caption = "Table of Estimates and Std. Errors")
    knitr::kable(exp(coef(data_out))[-1], caption = "Table of probability coefficients")
    knitr::kable(exp(suppressMessages(confint(data_out)))[-1,], caption = "Table of confidence intervals")
    
```

# Analysis

## Hypothesis Testing

### Kills

**Ho:** There is no statistically significant Kills effect on odds of winning.

**Ha:** There is a statistically significant Kills effect on odds of winning.

**z value:** 2.095

**p-value: ** .0362

**Formal Conclusion:** We reject Ho in favor of Ha: There is a statistically significant Kills effect on odds of winning at the .05 confidence level.

**Informal Conclusion:** There is a statistically significant Kills effect on odds of winning(p-value = .0362).

**Effect: ** Holding all else constant, for a one unit increase in Kills we estimate an expected 28.9% increase in odds of winning(95% CI: 2.2, 65.3).

### Deaths

**Ho:**There is no statistically significant Deaths effect on odds of winning.

**Ha:**There is a statistically significant Deaths effect on odds of winning.

**z value:** -3.807

**p-value: **.000141

**Formal:** We reject Ho in favor of Ha: There is a statistically significant Deaths effect on odds of winning at the .05 confidence level.

**Informal:** There is a statistically significant Deaths effect on odds of winning(p-value = .000141).

**Effect: ** holding all else constant, for a 1 unit increase in Deaths, we estimate an expected 25.1% decrease in odds of winning(95% CI: 13.9, 36.2). 

### Assists

**Ho:**There is no statistically significant Assists effect on odds of winning.

**Ha:**There is a statistically significant Assists effect on odds of winning.

**z-value:** 3.006
**p-value:** .002649
**Formal:** We reject Ho in favor of Ha: There is a statistically significant Assists effect on odds of winning at the .05 significance level

**Informal:** There is a statistically significant Assists effect on odds of winning(p-value = .0026).

**Effect:** holding all else constant, for a 1 unit increase in Assists, we estimate an expected decrease in odds of winning by 37.1%(95% CI: 12.7, 70.4).

### Headshots Landed

**Ho:**There is no statistically significant headshotsLanded effect on odds of winning.

**Ha:**There is a statistically significant headshotsLanded effect on odds of winning.

**z value:** 1.057

**p-value: ** .290

**Formal Conclusion:** We fail to reject Ho: There is no statistically significant headshotsLanded effect on odds of winning at the .05 significance level.

**Informal Conclusion:** There is no statistically significant headshotsLanded effect on odds of winning(p-value = .290).

**Effect: ** Holding all else constant, for a 1 unit increase in headshotsLanded, we estimate an expected increase in odds of winning by 5.5%(95% CI: -4.4, 16.6). However, there is not enough evidence to support a headshotsLanded effect.

### Kills Per Minute

**Ho:**There is no statistically significant killsPerMinute effect on odds of winning.

**Ha:**There is a statistically significant killsPerMinute effect on odds of winning.

**z value:** -0.245

**p-value: ** .807

**Formal Conclusion:** We fail to reject Ho:There is no statistically significant killsPerMinute effect on odds of winning at the .05 significance level.

**Informal Conclusion:** There is no statistically significant killsPerMinute effect on odds of winning(p-value = .807)

**Effect: ** Holding all else constant, for a 1 unit increase in killsPerMinute, we estimate an expected decrease in odds of winning by 11.6%(95% CI: -66.9, 141.96). However, there is not enough evidence to support a killsPerMinute effect.

### Distance Portaled

**Ho:**There is no statistically significant distancePortaled effect on odds of winning

**Ha:**There is a statistically significant distancePortaled effect on odds of winning

**z value:** .924

**p-value: ** .356

**Formal Conclusion:** We fail to reject Ho:There is no statistically significant distancePortaled effect on odds of winning at the .05 significance level

**Informal Conclusion:** There is no statistically significant distancePortaled effect on odds of winning(p-value = .356)

**Effect: ** Holding all else constant, for a 1 unit increase in distancePortaled, we estimate an expected increase in odds of winning by 5.5%(95% CI: -4.4, 16.6). However, there is not enough evidence to support a headshotsLanded effect.

### Portals Spawned

**Ho:**There is no statistically significant headshotsLanded effect on odds of winning

**Ha:**There is a statistically significant headshotsLanded effect on odds of winning

**z value:** 1.057

**p-value: ** .290

**Formal Conclusion:** We fail to reject Ho:There is no statistically significant headshotsLanded effect on odds of winning at the .05 significance level

**Informal Conclusion:** There is no statistically significant headshotsLanded effect on odds of winning(p-value = .290)

**Effect: ** Holding all else constant, for a 1 unit increase in headshotsLanded, we estimate an expected increase in odds of winning by 5.5%(95% CI: -4.4, 16.6). However, there is not enough evidence to support a headshotsLanded effect.

### Damage Dealt

**Ho:**There is no statistically significant headshotsLanded effect on odds of winning

**Ha:**There is a statistically significant headshotsLanded effect on odds of winning

**z value:** 1.057

**p-value: ** .290

**Formal Conclusion:** We fail to reject Ho:There is no statistically significant headshotsLanded effect on odds of winning at the .05 significance level

**Informal Conclusion:** There is no statistically significant headshotsLanded effect on odds of winning(p-value = .290)

**Effect: ** Holding all else constant, for a 1 unit increase in headshotsLanded, we estimate an expected increase in odds of winning by 5.5%(95% CI: -4.4, 16.6). However, there is not enough evidence to support a headshotsLanded effect.






